Article Title

### 2013-08-01 sections/Theory.tex
minor

\subsection{Covariance estimation}

@@

An unbiased estimate does not guarantee lack of bias in nonlinear functions of that estimate: $\mathbb E\left[\hat\Sigma_0\right]=0 \centernot\implies  E\left[\varphi(\hat\Sigma_0\right)]=0$, where $\varphi$ is a nonlinear function.

@@

\paragraph{Constructing a regularized estimator:}
The task of designing a regularized estimators consists of defining a sequence of approximations $\hat\Sigma_\gamma$, called \emph{regularization path} and the optimal location on that path, \emph{regularization intensity} $\hat\gamma$ as  functions of the empirical distribution.

>>>>

\subsection{Theory and notation}

@@

An unbiased estimate does not guarantee lack of bias in nonlinear functions of that estimate: $\mathbb E\left[\hat\Sigma_0\right]=\Sigma \centernot\implies  E\left[\varphi(\hat\Sigma_0)\right]=\varphi(\Sigma)$, where $\varphi$ is a nonlinear function. For example, if $u_{\max}(S)$ is the largest eigevalue of square matrix $S$, then $\mathbb E\left[u_{\max}(\hat\Sigma_0)\right] > u_{\max}(\Sigma)$. Some regularization schemes have been designed to correct for the eigenspectrum bias  at the cost of adding bias to covariance coefficients \citep{Ledoit:2004}.

@@

\subsection{Regularized covariance estimates}
The task of designing a regularized estimators consists of defining a sequence of approximations $\hat\Sigma_\gamma$, called \emph{regularization path} and the optimal location on that path, \emph{regularization intensity} $\hat\gamma$ as  functions of the empirical distribution.
